Supplementary Material for: A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2021-05-04 supplement/06_bat_data.Rmd
move code to supplement

```{r echo=FALSE, eval=TRUE}
# not shown or mentioned
fig_bat_res_timeseries <-
  ggplot() +
  geom_path(
    data = data_residence,
    aes(ts, resTime,
      colour = TAG
    ),
    show.legend = F
  ) +
  scale_color_brewer(palette = "Dark2") +
  scale_x_datetime() +
  ggthemes::theme_few() +
  labs(
    x = NULL,
    y = "residence time (mins)"
  )
```

@@

```{r}
st_write(data_spatials,
  dsn = "data/data_bat_residence_patches.gpkg",
  append = FALSE
)
```

>>>>

```{r echo=FALSE, eval=FALSE}
# not shown or mentioned
fig_bat_res_timeseries <-
  ggplot() +
  geom_path(
    data = data_residence,
    aes(ts, resTime,
      colour = TAG
    ),
    show.legend = F
  ) +
  scale_color_brewer(palette = "Dark2") +
  scale_x_datetime() +
  ggthemes::theme_few() +
  labs(
    x = NULL,
    y = "residence time (mins)"
  )
```

@@

```{r}
st_write(data_spatials,
  dsn = "data/data_bat_residence_patches.gpkg"
)
```
